A Linked Open Social Dataset for Scientific Benchmarking

### 2019-06-29 mdpi/template.tex
iniciada passagem do artigo para o template do Data

\documentclass[review]{elsarticle}

\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[dvipsnames]{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black},
    pdfborder={0 0 0}
}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{float}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
% \usepackage[T1]{fontenc}
% \usepackage{changepage}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{listings}
\lstdefinelanguage[]{spq}
{
    morecomment=[s][\color{ForestGreen}\bf]{<}{>},
    basicstyle = \ttfamily\footnotesize,
    commentstyle=\color{green},
    keywordstyle=\color{Plum},
    morecomment=[s][\color{Blue}\bf]{?}{\ },
    morekeywords={BASE,PREFIX,SELECT,DISTINCT,CONSTRUCT,DESCRIBE,ASK,%
    FROM,NAMED,WHERE,ORDER,BY,ASC,DESC,LIMIT,OFFSET,OPTIONAL,%
    GRAPH,UNION,FILTER,a,STR,LANG,LANGMATCHES,DATATYPE,BOUND,%
    isIRI,isURI,isBLANK,isLITERAL,REGEX,true,false},%
    sensitive=false,%
    % morecomment=[l]\#,%
    morestring=[d][\color{red}]',%
    morestring=[d]"%
}
% \usepackage[showframe=true]{geometry}
%

\newcommand{\textttt}[1] {\texttt{\footnotesize#1}}
\newcommand{\te}[1] {\texttt{\footnotesize#1}}
\newcommand{\h} {\hphantom ~ }
% \newcommand{\textttt}[1] {\mbox{\texttt{\footnotesize#1}}}
% \newcommand{\textttt}[1] {
% \begin{verbatim} #1 \end{verbatim}
% }
\linespread{1}
\pgfplotsset{compat=1.5}
\pgfplotsset
{
	width=0.5\textwidth,
	x tick label style={/pgf/number format/1000 sep=},
  enlarge x limits = 0.0,
  ymajorgrids=true,
	major tick style={draw=none},
  ymin = 0.0,
	every axis/.append style={
		every x tick label/.append style={font=\tiny},
    every y tick label/.append style={font=\tiny},
    every axis label/.append style={font=\small},
    height=37mm,
    width=37mm,
    title style={at={(0.5,0.90)}, font=\normalfont},
    xticklabel style={yshift=4pt}
	}
}
\usepackage{booktabs}
%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%
\makeatletter
\def\ps@pprintTitle{%
    \let\@oddhead\@empty
    \let\@evenhead\@empty
    \def\@oddfoot{}%
\let\@evenfoot\@oddfoot}
\makeatother
\begin{document}
%
\begin{frontmatter}
%
\title{A Linked Open Social Dataset for Scientific Benchmarking}
%
\author[pws]{Renato Fabbri\corref{corresponding}}
\ead{renato.fabbri@gmail.com}
%
\author[pwr]{Osvaldo Novais de Oliveira Junior}
\ead{chu@ifsc.usp.br}
%
\cortext[corresponding]{Corresponding author}
  \address[pws]{Institute of Mathematics and Computer Sciences, University of São Paulo (ICMC/USP), Brazil}
\address[pwr]{S\~ao Carlos Institute of Physics, University of  São Paulo
(IFSC-USP), Brazil}
%
\begin{abstract}
The fields of social network analysis and complex networks
are widely researched.
In fact, a myriad of results have been reported which are based in
diverse data, most often not accessible to researchers other than the publishing authors.
This work presents an open dataset with diverse provenance of 
human social online networking 
  and oriented
to furnish the scientific community with a friendly and common repertoire.
Current data was obtained in 2013-16 from well-known online social networking platforms:
Facebook, Twitter, IRC, Email.
Data from ParticipaBR, AA, and Cidade Democrática were also added as samples of
less known instances.
Authors recently recognized that no similar dataset was made available,
and the potential benefit of the content for the research community.
The linked data representation was adopted in order to
comply with current best practices, homogenize access, enable discovery,
and facilitate analyzes which integrate third
party and provided instances.
Futhermore, the method for obtaing and making the data available is potentially novel, and may of use for other research groups.
This document presents an outline and overall statistics of the given
dataset, which should favor subsequent work in complex and social networks,
  and in enhancing the available linked and social data.
\end{abstract}
%
\begin{keyword}
Big Data, Dataset, Benchmark Data, Facebook, Twitter, IRC, Email,
Complex Networks, Social Networks, Text Mining
%Hierarchy of Clusters \sep HoC \sep Benchmark Dataset \sep Benchmark Data Generator \sep Artificial Data \sep Cluster Analysis \sep Tree Structured Stick Breaking Process \sep TSSB \sep ...
\end{keyword}

\end{frontmatter}

\section{Introduction}
% In recent years, the web of linked data~\cite{lee1} has attracted wide attention in
% both research and application realms.
The research on human social and complex networks often realy on data that express
real phenomena~\cite{c1,c2,c3}.
Such data is often not made publicly available, which hinders validation of the results and does not favor makes subsequent work.
Furthermore, there is a lack of open datasets for benchmarking results,
specially associated to the complex and social networks field,
yielding diverse results from poorly related sources.
Scarce and historical exceptions are the karate club or the dolphin datasets~\cite{newmanBook,dolphin}.
For expressing the information,
open machine-readable content and tools are desired for enabling
data linkage and discovery~\cite{o1,o2},
and the favoured protocol is thus RDF ``linked data''.
Social networks linked data is currently not stable or rigorous enough to be
a public reference on statistical physics and social networks research,
with scarce exceptions~\cite{l1,l2}
This work presents a collection of linked and open data
about online human social networks,
named LOSD (Linked Open Social Data).
This has been achieved by linking social data into a dataset using diverse
provenance, namely: Facebook, Twitter, IRC, Email groups, ParticipaBR, Cidade Democrática, and AA.
Such data is proposed as a common and public repertoire for scientific
research involving networks and textual content.

\subsection{Related work}
Most available datasets on human social networks rely on only one source~\cite{o1,o2,o3,o4},
on specialized communities such as related to research and movies~\cite{s1,s2,s3,s4,s5},
or present only statistics about social networks, and not the data that yields the networks~\cite{st1,st2,st3,st4}.
Contributions which are most similar to LOSD are mentioned in this section.
In~\cite{fb1}, data obtained only from Facebook is reported.
With such a focus, the authors make available a number of statistics,
but the data is offline at least since 2010.
Linked human social network data is scarcely found in the scientific community.
In~\cite{foaf1}, the authors presented a set of tools to obtain linked social data available in the public data cloud, and made available a dataset from the Advogato platform,
dedicated to free software developers linked by trust relatioships.
There are various datasets which makes available data obtained from Twitter (e.g.~\cite{tw1,tw2,t3,t4}),
most often with a specific focus (users, tweets, hashtags, etc)
and not presented to the scientific community by means of a research article.
In summary, no human social network dataset presented to the
scientific community containts the diverse provenance used in LOSD,
potentially because researchers did not have the means to acquire and
share the data described in Section~\ref{acq}.

% \subsection{Benchmarking in the analysis of complexity}

\section{Methods}
LOSD is expressed as linked data through RDF
and is ontologicaly described through the
data-driven ontology synthesis method presented in Section~\ref{ont}.

@@

\section{Materials}\label{materials}
Data was gathered from:
\begin{itemize}
    \item public APIs (Twitter, Email);
    \item public logs (IRC and AA);
    \item Netvizz software~\cite{netvizz} and subsequent donation by users (Facebook);
    \item donation by system administrators (AA, ParticipaBR, Cidade Democr\'atica).
\end{itemize}

\section{Results}
\label{outline}
Current overall results concern data selection and preparation for data discovery.
The main result is the data made available, which enables benchmarking of scientific results
and easy experimentations, and no compliant dataset was found by the authors.
Secondary results include data outline through figures and tables,
software support and example SparQL queries.

\subsection{Data outline}
\input{misc/overallText}

\input{tables/nsnapshots}
% stats:
%% number of triples
%% number of edges
%% number of chars
%% number of users
% diagrams in the supporting information file
\subsection{Software tools}
The authors made available software for rendering analyses and
the data set itself.
\subsubsection{Triplification routines}
For each social platform there is a \emph{triplification} routine,
i.e. a script for expressinf the data as RDF.
Original formats and further observations are presented in
Table~\ref{tab:provenance}.
  {\renewcommand{\arraystretch}{1.2}
\begin{table*}[h!]\scriptsize
\begin{center}
\caption{Social platforms, original formats and further observations for
the database.}\label{tab:provenance}
\begin{tabular}{ l | p{3cm} p{3cm} c }
    \textbf{social platform} & \textbf{original format} & \textbf{further observations} & \textbf{toolbox} \\\specialrule{1.5pt}{1pt}{1pt}
    AA & MySQL and MongoDB databases; IRC text logs & donated by AA users & Participation~\cite{participation} \\\hline
    Cidade Democrática & MySQL database & donated by admins & Participation \\\hline
    Email & mbox & obtained through the Gmane public archive & Gmane~\cite{gmane} \\\hline
    Facebook & GDF, GML and TAB & obtained through Netvizz~\cite{netvizz} & Social~\cite{social} \\\hline
    IRC & plain text log & obtained through Supybot logging & Social \\\hline
    ParticipaBR & PostgreSQL database & donated by admins & Participation \\\hline
    Twitter & JSON & obtained through Twitter streaming API & Social \\
\end{tabular}\end{center}
\end{table*}                    
  }
\subsubsection{Topological and textual analysis}\label{ana}
Routines are available for taking topological and textual measures from
the LOSD data.
  Auxiliary routines, such as for performing principal component analysis (PCA)
  and obtaining statistics derived from the Kolmogorov-Smirnov test~\cite{kol}, are available to ease pattern recognition.

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[width=0.5\textwidth]{ontologies/facebook-legacy-AntonioAnzoategui18022013Friendship.ttl/draw}
    \caption{A diagram of the core structure that entails the friendship networks
    of the Facebook snapshots. A green edge denotes an OWL existential class restriction; an inverted nip denotes an OWL universal class restriction; a full (non-dashed) edge denotes an OWL functional property axiom (see Section~\ref{sont}). Further information and complete diagrams for each provenance are available in the Supporting Information document.}\label{dia}
\end{figure}

@@

Again, this is not an exaustive list.
For example, other instances which are related in LOSD, and have authors,
also yield valid criteria for interaciton networks.
For a less canonical example for obtaining networks, links may be derived from sufficiently similar vocabulary used by participants, or from activity is sufficiently similar dates, which yield networks which are not interaction or friendship networks.
% mk figure with two participants and their relation though response, retweet, or friendship

\section{License issues}
% Facebook, Twitter, IRC, Gmane, Participa, CD, AA.
The data presented in this article is released under public domain.
Computer scripts are in git repositories and PyPI Python packages, also under public domain.
Although most data is already in open licenses (Twitter, Email, Participabr, Cidade Democrática, and AA data), IRC and Facebook data was collected
and donated by the individuals which yield the data, in a practice compliant with the framework described in Section~\ref{acq}.
% Of central importance to the obtainment of the data is the concept of
% anthropological physics~\cite{antphy}
\section{Conclusions}
\label{conclusions}
This article outlines LOSD, a large human online social networking dataset (with almost 35 million triples) with diverse provenance.
Tools and procedures used to achieve LOSD, and fundamental queries needed to retrieve the data, are also described to the convenience of the newcommer
and for a consistent exposition.
The resulting dataset should be expanded upon need or request from interested parties.
All data should be available online in the \url{http://linkedopensocialdata.org}
address in near future to fulfill the purpose of being a common
repertoire in current research.
All data is publicly available though the endpoint \url{xxxyyyzzz},
through which the scientific community now has consistent and curated data
that enables research validation, continuity, and benchmarking.
The diagrams and tables of the Supporting Information document of this article
for further directions
on the available structures and for an overview complement.

% further work: link participants in Facebook with those in ParticipaBR, for example
% crowsorce more data
% assure data is 5 starts TTM

% Supporting Information
% diverse provenance, large database, should be expanded, waits feedback
\section*{References}
%
% \bibliographystyle{plainurl}
\bibliography{paper}
%\bibliography{myLastBibfile.bib}
%
\end{document}

>>>>

%  LaTeX support: latex@mdpi.com 
%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).

%=================================================================
\documentclass[journal,article,submit,moreauthors,pdftex]{Definitions/mdpi}

\usepackage{enumitem}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black},
    pdfborder={0 0 0}
}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{float}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
% \usepackage[T1]{fontenc}
% \usepackage{changepage}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{listings}
\lstdefinelanguage[]{spq}
{
    morecomment=[s][\color{olive}\bf]{<}{>},
    basicstyle = \ttfamily\footnotesize,
    commentstyle=\color{green},
    keywordstyle=\color{brown},
    morecomment=[s][\color{blue}\bf]{?}{\ },
    morekeywords={BASE,PREFIX,SELECT,DISTINCT,CONSTRUCT,DESCRIBE,ASK,%
    FROM,NAMED,WHERE,ORDER,BY,ASC,DESC,LIMIT,OFFSET,OPTIONAL,%
    GRAPH,UNION,FILTER,a,STR,LANG,LANGMATCHES,DATATYPE,BOUND,%
    isIRI,isURI,isBLANK,isLITERAL,REGEX,true,false},%
    sensitive=false,%
    % morecomment=[l]\#,%
    morestring=[d][\color{red}]',%
    morestring=[d]"%
}
% \usepackage[showframe=true]{geometry}
%

\newcommand{\textttt}[1] {\texttt{\footnotesize#1}}
\newcommand{\te}[1] {\texttt{\footnotesize#1}}
\newcommand{\h} {\hphantom ~ }
% \newcommand{\textttt}[1] {\mbox{\texttt{\footnotesize#1}}}
% \newcommand{\textttt}[1] {
% \begin{verbatim} #1 \end{verbatim}
% }
\linespread{1}
\pgfplotsset{compat=1.5}
\pgfplotsset
{
	width=0.5\textwidth,
	x tick label style={/pgf/number format/1000 sep=},
  enlarge x limits = 0.0,
  ymajorgrids=true,
	major tick style={draw=none},
  ymin = 0.0,
	every axis/.append style={
		every x tick label/.append style={font=\tiny},
    every y tick label/.append style={font=\tiny},
    every axis label/.append style={font=\small},
    height=37mm,
    width=37mm,
    title style={at={(0.5,0.90)}, font=\normalfont},
    xticklabel style={yshift=4pt}
	}
}
\usepackage{booktabs}
% If you would like to post an early version of this manuscript as a preprint, you may use preprint as the journal and change 'submit' to 'accept'. The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, aerospace, agriculture, agriengineering, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, asc, asi, atmosphere, atoms, axioms, batteries, bdcc, behavsci , beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci , buildings, cancers, carbon , catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, children, cleantechnol, climate, clockssleep, cmd, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, dairy, data, dentistry, designs , diagnostics, diseases, diversity, drones, econometrics, economies, education, ejihpe, electrochem, electronics, energies, entropy, environments, epigenomes, est, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forests, fractalfract, futureinternet, futurephys, galaxies, games, gastrointestdisord, gels, genealogy, genes, geohazards, geosciences, geriatrics, hazardousmatters, healthcare, heritage, highthroughput, horticulturae, humanities, hydrology, ijerph, ijfs, ijgi, ijms, ijns, ijtpp, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jcdd, jcm, jcp, jcs, jdb, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmse, jnt, jof, joitmc, jpm, jrfm, jsan, land, languages, laws, life, literature, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, mathematics, mca, medicina, medicines, medsci, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, modelling, molbank, molecules, mps, mti, nanomaterials, ncrna, neuroglia, nitrogen, notspecified, nutrients, ohbm, optics, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, physics, plants, plasma, polymers, polysaccharides, preprints , proceedings, processes, proteomes, psych, publications, quantumrep, quaternary, qubs, reactions, recycling, religions, remotesensing, reports, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, signals, sinusitis, smartcities, sna, societies, socsci, soilsystems, sports, standards, stats, surfaces, surgeries, sustainability, symmetry, systems, technologies, test, toxics, toxins, tropicalmed, universe, urbansci, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wem, wevj

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, conferenceproceedings, correction, conferencereport, expressionofconcern, extendedabstract, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, meetingreport, newbookreceived, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, supfile, technicalnote, viewpoint
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{xx}
\issuenum{1}
\articlenumber{5}
\pubyear{2019}
\copyrightyear{2019}
%\externaleditor{Academic Editor: name}
\history{Received: date; Accepted: date; Published: date}
%\updates{yes} % If there is an update available, un-comment this line

%% MDPI internal command: uncomment if new journal that already uses continuous page numbers 
%\continuouspages{yes}

%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{A Linked Open Social Dataset for Scientific Benchmarking}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{https://orcid.org/0000-0002-9699-629X} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{https://orcid.org/0000-0002-5399-5860} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Renato Fabbri $^{1}$*\orcidA{} and Osvaldo N. Oliveira Junior $^{2}$\orcidB{}}

% Authors, for metadata in PDF
\AuthorNames{Renato Fabbri, Osvaldo Novais de Oliveira Junior}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Institute of Mathematical and Computer Sciences, University of São Paulo (ICMC/USP), São Carlos, Brazil; renato.fabbri@gmail.com\\
$^{2}$ \quad São Carlos Institute of Physics, University of São Paulo (IFSC/USP), São Carlos, Brazil; chu@ifsc.usp.br}

% Contact information of the corresponding author
\corres{Correspondence: renato.fabbri@gmail.com}

% Current address and/or shared authorship
% \firstnote{Current address: Affiliation 3} 
% \secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{
The fields of social network analysis and complex networks
are widely researched.
In fact, a myriad of results have been reported which are based in
diverse data, most often not accessible to researchers other than the publishing authors.
In order to furnish the scientific community with a common repertoire,
this work presents an open dataset with diverse provenance of 
human social online networking.
Current data was obtained in 2013-16 from well-known online social networking platforms:
Facebook, Twitter, IRC, Email.
Data from ParticipaBR, AA, and Cidade Democrática are also supplied as samples of less known instances.
The linked data representation was adopted in order to
comply with current best practices, homogenize access, facilitate discovery
and analyzes which integrate third party and provided instances.
Futhermore, the method for obtaing and making the data available is potentially novel, and may of use for other research groups.
This document presents a description, usage remarks and overall statistics of the dataset, which should favor subsequent work in complex and social networks
  and enhancements to the dataset.
}

% Keywords
\keyword{social networks; complex networks; linked data; semantic web; big data; benchmark data; Facebook; Twitter; irc; email}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
\dataset{https://rfabbri.linked.data.world/d/linked-open-social-data/}

\datasetlicense{CC0}

\begin{document}
\section{Summary}
The research on human social and complex networks often rely on data that express real phenomena~\cite{c1,c2,c3}.
Such data is regularly not made publicly available,
which hinders validation of the results
and does not favor subsequent work.
Furthermore, there is a lack of open datasets for benchmarking results
related to complex and social networks,
yielding diverse results from poorly related sources.
Social networks linked data is currently scarce and not stable
or rigorous enough to be a public reference on statistical physics
and social networks research~\cite{l1,l2}.

This work presents a collection of linked and open data
derived from online human social networks.
The dataset is named LOSD (Linked Open Social Data),
and has been achieved by linking social data into a dataset derived from diverse
provenance, namely: Facebook, Twitter, IRC, Email groups, ParticipaBR, Cidade Democrática, and AA.
Such data is proposed as a common and public repertoire for scientific
research involving networks and textual content.
In fact, the data has already been used in scientific research~\cite{stab,thesis} (CNPq grant ), and should be used in further research in complex networks and data visualization (FAPESP grant ) which relies on networks enriched by textual data and on dynamic (or time-evolving) networks.

\subsection{Related work}
Most available datasets on human social networks rely on only one source~\cite{o1,o2,o3,o4},
on specialized communities such as related to research and movies~\cite{s1,s2,s3,s4,s5},
or present only statistics about social networks, and not the data that yields the networks~\cite{st1,st2,st3,st4}.
Contributions which are most similar to LOSD are mentioned in this section.
In~\cite{fb1}, data obtained only from Facebook is reported.
With such a focus, the authors made available a number of statistics,
but the data is offline at least since 2010.
Linked human social network data is scarcely found in the scientific community.
In~\cite{foaf1}, the authors presented a set of tools to obtain linked social data available in the public data cloud, and made available a dataset from the Advogato platform,
dedicated to free software developers linked by trust relatioships.
There are various datasets which makes available data obtained from Twitter (e.g.~\cite{tw1,tw2,t3,t4}),
most often with a specific focus (users, tweets, hashtags, etc)
and not presented to the scientific community by means of a research article.
In summary, no human social network dataset presented to the
scientific community containts the diverse provenance used in LOSD,
potentially because researchers did not have the means to acquire and
share the data as described in Section~\ref{acq}.

\section{Data Description}\label{materials}
\subsection{Data outline}
\input{../misc/overallText}

\input{../tables/nsnapshots}
\label{outline}
Current overall results concern data selection and preparation for data discovery.
The main result is the data made available, which enables benchmarking of scientific results
and easy experimentations, and no compliant dataset was found by the authors.
Secondary results include data outline through figures and tables,
software support and example SparQL queries.

Data was gathered from:
\begin{itemize}
    \item public APIs (Twitter, Email);
    \item public logs (IRC and AA);
    \item Netvizz software~\cite{netvizz} and subsequent donation by users (Facebook);
    \item donation by system administrators (AA, ParticipaBR, Cidade Democr\'atica).
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methods}
LOSD is expressed as linked data through RDF
and is ontologicaly described through the
data-driven ontology synthesis method presented in Section~\ref{ont}.

@@

\section{Usage notes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt} 
\subsection{Software tools}
The authors made available software for rendering analyses and
the data set itself.
\subsubsection{Triplification routines}
For each social platform there is a \emph{triplification} routine,
i.e. a script for expressinf the data as RDF.
Original formats and further observations are presented in
Table~\ref{tab:provenance}.
  {\renewcommand{\arraystretch}{1.2}
\begin{table*}[h!]\scriptsize
\begin{center}
\caption{Social platforms, original formats and further observations for
the database.}\label{tab:provenance}
\begin{tabular}{ l | p{3cm} p{3cm} c }
    \textbf{social platform} & \textbf{original format} & \textbf{further observations} & \textbf{toolbox} \\\specialrule{1.5pt}{1pt}{1pt}
    AA & MySQL and MongoDB databases; IRC text logs & donated by AA users & Participation~\cite{participation} \\\hline
    Cidade Democrática & MySQL database & donated by admins & Participation \\\hline
    Email & mbox & obtained through the Gmane public archive & Gmane~\cite{gmane} \\\hline
    Facebook & GDF, GML and TAB & obtained through Netvizz~\cite{netvizz} & Social~\cite{social} \\\hline
    IRC & plain text log & obtained through Supybot logging & Social \\\hline
    ParticipaBR & PostgreSQL database & donated by admins & Participation \\\hline
    Twitter & JSON & obtained through Twitter streaming API & Social \\
\end{tabular}\end{center}
\end{table*}                    
  }
\subsubsection{Topological and textual analysis}\label{ana}
Routines are available for taking topological and textual measures from
the LOSD data.
  Auxiliary routines, such as for performing principal component analysis (PCA)
  and obtaining statistics derived from the Kolmogorov-Smirnov test~\cite{kol}, are available to ease pattern recognition.

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[width=0.5\textwidth]{../ontologies/facebook-legacy-AntonioAnzoategui18022013Friendship.ttl/draw}
    \caption{A diagram of the core structure that entails the friendship networks
    of the Facebook snapshots. A green edge denotes an OWL existential class restriction; an inverted nip denotes an OWL universal class restriction; a full (non-dashed) edge denotes an OWL functional property axiom (see Section~\ref{sont}). Further information and complete diagrams for each provenance are available in the Supporting Information document.}\label{dia}
\end{figure}

@@

Again, this is not an exaustive list.
For example, other instances which are related in LOSD, and have authors,
also yield valid criteria for interaciton networks.
For a less canonical example for obtaining networks, links may be derived from sufficiently similar vocabulary used by participants, or from activity is sufficiently similar dates, which yield networks which are not interaction or friendship networks.
% mk figure with two participants and their relation though response, retweet, or friendship TTM

\section{Conclusions and further work}
\label{conclusions}
This article outlines LOSD, a large human online social networking dataset (with almost 35 million triples) with diverse provenance.
Tools and procedures used to achieve LOSD, and fundamental queries needed to retrieve the data, are also described to the convenience of the newcommer
and for a consistent exposition.
The resulting dataset should be expanded upon need or request from interested parties.
All data should be available online in the \url{http://linkedopensocialdata.org}
address in near future to fulfill the purpose of being a common
repertoire in current research.
All data is publicly available though the endpoint \url{xxxyyyzzz},
through which the scientific community now has consistent and curated data
that enables research validation, continuity, and benchmarking.
The diagrams and tables of the Supporting Information document of this article
for further directions
on the available structures and for an overview complement.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{Conceptualization, writing, formal analysis, R.F; senior supervision, final writing, O.N.O.Jr.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\funding{This research was funded by CNPq (grant number XXX) and FAPESP (grant number ).}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{The authors thank all participants in the experiments which  donated the data they gathered as described in Section~\ref{}.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{The authors declare no conflict of interest. The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, or in the decision to publish the results.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\appendixtitles{no} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendix
\section{}
\unskip
\subsection{}
The appendix is an optional section that can contain details and data supplemental to the main text. For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data. Mathematical proofs of results not central to the paper can be added as an appendix.

\section{}
All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
%=====================================
\externalbibliography{yes}
\bibliography{../paper}

%=====================================
% References, variant B: internal bibliography
%=====================================
% \begin{thebibliography}{999}
% % Reference 1
% \bibitem[Author1(year)]{ref-journal}
% Author1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
% % Reference 2
% \bibitem[Author2(year)]{ref-book}
% Author2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
% \end{thebibliography}

% The following MDPI journals use author-date citation: Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences. For those journals, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\sampleavailability{Samples of the compounds ...... are available from the authors.}

%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
